Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
wording

The final case we analyze is that of hybrid-time models, where the plant
dynamics evolve in continuous time while the feedback dynamics evolve in
discrete time.  A~new input value is produced only at every sample time but
implemented over the continuous-time plant dynamics.
%
\begin{theorem}
The expression
%
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
%
with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s},
\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
sample time $T_s$, is the state of the model
%
\begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s \,. 
\end{align*}
%
For the proof see Appendix~\ref{sec:proofs}
%
\end{theorem}
%\begin{proof}
%See Appendix~\ref{sec:proofs}
%\end{proof}

@@

Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
representing the binary word length of the representation and $F$ bits
representing the pre-scaling $2^{-F}$ (\emph{i.e} the number of bits after
the decimal place).  We note that a negative $F$ denotes an integer
multiplication that adds $-F$ trailing zeros in the number represented
by~$M$.  We will use the domain $\mathbb{R}_{\langle C \rangle}
\text{ where } \langle C \rangle = \langle M_c,F_c \rangle$ to represent the fixed point
precision of the controller, and $\mathbb{R}_{\langle P \rangle} \supseteq
\mathbb{R}_{\langle C \rangle}$ to represent the domain of a digital model
of the dynamics of a real plant when evaluated by a verification tool. 
Elements in this domain are marked with an underscore~${\langle C \rangle}$
(see Figure \ref{fig:observersystem}).  Thus, any mathematical operation
within the digital controller is executed in the domain $\mathbb{R}_{\langle
C \rangle}$, and all other calculations in our model will be carried out in
the domain $\mathbb{R}_{\langle P \rangle}$.  Given ${\langle M,F \rangle}$,
we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow
\mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function.  We
further note that the results of mathematical operations in these domains
are also truncated.  This is referred to as roundoff errors.

@@

Stability qualitatively denotes the property of a model to evolve within a
bounded set around an equilibrium point.  In this paper, we are interested
in asymptotic stability, where the model is further expected to converge to
the steady state value (i.e., the equilibrium point).
%
We specify model stability via Jury's criterion~\cite{fadali}, 
as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
which boils down to a requirement expressed as an algebraic formula on the
characteristic polynomial of the model.  In order to facilitate the use of
Jury's criterion, we transform the model into a representation that contains
the coefficients of its characteristic polynomial expressed as sums of
controller and plant values.  The benefit of this representation is that it
has no multiplications, which are expensive to handle by SAT solvers (used
by the synthesizer).
%
Such a representation is a model known as 
% is called Controllable and Observable 
``canonical form''~\cite{Astrom08} %\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
and is dynamically equivalent to the given model.  
In this section we explore the implications of using the canonical form, 
alongside the use of FWL representations.

>>>>

The final case we analyze is that of hybrid-time models, where the plant
dynamics evolve in continuous time while the feedback dynamics evolve in
discrete time.  A~new input value is produced only at every sample time but
implemented over the continuous-time plant dynamics.
%
\begin{theorem}
The expression
%
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
%
with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s},
\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
sample time $T_s$, is the state of the model
%
\begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s \,. 
\end{align*}
%
For the proof see Appendix~\ref{sec:proofs}.
%
\end{theorem}
%\begin{proof}
%See Appendix~\ref{sec:proofs}
%\end{proof}

@@

Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
representing the binary word length of the representation and $F$ bits
representing the pre-scaling $2^{-F}$ (i.e., the number of bits after
the decimal place).  We note that a negative $F$ denotes an integer
multiplication that adds $-F$ trailing zeros in the number represented
by~$M$.  We will use the domain $\mathbb{R}_{\langle C \rangle}
\text{ where } \langle C \rangle = \langle M_c,F_c \rangle$ to represent the fixed point
precision of the controller, and $\mathbb{R}_{\langle P \rangle} \supseteq
\mathbb{R}_{\langle C \rangle}$ to represent the domain of a digital model
of the dynamics of a real plant when evaluated by a verification tool. 
Elements in this domain are marked with an underscore~${\langle C \rangle}$
(Figure~\ref{fig:observersystem}).  Thus, any mathematical operation
within the digital controller is executed in the domain $\mathbb{R}_{\langle
C \rangle}$, and all other calculations in our model will be carried out in
the domain $\mathbb{R}_{\langle P \rangle}$.  Given ${\langle M,F \rangle}$,
we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow
\mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function.  We
further note that the results of mathematical operations in these domains
are also truncated.  This is referred to as roundoff errors.

@@

Stability qualitatively denotes the property of a model to evolve within a
bounded set around an equilibrium point.  In this paper, we are interested
in asymptotic stability, where the model is further expected to converge to
the steady state value (i.e., the equilibrium point).
%
We specify model stability via Jury's criterion~\cite{fadali}, 
as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
which is given as a requirement expressed as an algebraic formula on the
characteristic polynomial of the model.  In order to facilitate the use of
Jury's criterion, we transform the model into a representation that contains
the coefficients of its characteristic polynomial expressed as sums of
controller and plant values.  The benefit of this representation is that it
has no multiplications, which are expensive to handle by SAT solvers (used
by the synthesizer).
%
Such a representation is a model known as 
% is called Controllable and Observable 
``canonical form''~\cite{Astrom08} %\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
and is dynamically equivalent to the given model.  
In this section we explore the implications of using the canonical form, 
alongside the use of FWL representations.
